\section{\color{olive}Excercise 3: Four-Entry Encoder and Four-Output Demux using Verilog}
Implement the following modules in Verilog:
\begin {itemize}
\item 4 inputs \textsc{encoder}
\item 4 outputs \textsc{demux}
\end {itemize}

\subsection{\color{purple}4-Input ENCODER}
\subsubsection{\color{orange}Description}
An encoder is an Application-Specific Integrated Circuit (ASIC) that converts information. In this case it receives a signal from  a 4-bit input and returns the position of the Most Significant Bit that is currently on.
\subsubsection{\color{orange}Code Implementation}
The Code Implementation of both the Module and its testbench can be found in their respective directories.
\subsubsection{\color{orange}Module Tests}
\label{subsec1}
Testbench results can be found in Table \ref{subsec1}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Input&Output&Value\\
\hline
0001&00&0\\
0010&01&1\\
0100&10&2\\
1000&11&3\\
0011&01&1\\
0101&10&2\\
1001&11&3\\
0110&10&2\\
1010&11&3\\
1100&11&3\\
\hline
\end{tabular}
\\\vspace{12pt}
Table \ref{subsec1} \textsc{encoder} Testbench Results
\end{center}

\subsubsection{\color{orange}Conclusions}
The module is working as expected, where it is taking only the Most Significant Bit as the value to be encoded.

\subsection{\color{purple}4-output DEMUX}

\subsubsection{\color{orange}Description}
A DEMUX is an ASIC which receives an input signal and a selector signal. The selector signal determines through which output port the input signal is sent.

\subsubsection{\color{orange}Code Implementation}
The Code implementation for the \textsc{demux} can be found in its corresponding folder.

\subsubsection{\color{orange}Module Tests}
\label{subsec2}

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Input&Selector&Out\_0&Out\_1&Out\_2&Out\_3\\
\hline
1&0&1&0&0&0\\
1&1&0&1&0&0\\
1&2&0&0&1&0\\
1&3&0&0&0&1\\
\hline
\end{tabular}
\\\vspace{12pt}
Table \ref{subsec2} \textsc{demux} Testbench Results
\end{center}

\subsubsection{\color{orange}Conclusions}
The module works as expected.